---
output:
  pdf_document:
    citation_package: natbib
    latex_engine: pdflatex
    keep_tex: true
    includes:
        in_header: vignette_head.tex
title: "ATEHonest: Honest CIs for Average Treatment Effects"
author: "Michal Kolesár"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
bibliography: ate-library.bib
vignette: >
  %\VignetteIndexEntry{ATEHonest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, cache=FALSE}
library("knitr")
knitr::opts_knit$set(self.contained = FALSE)
knitr::opts_chunk$set(tidy = TRUE, collapse=TRUE, comment = "#>",
                      tidy.opts=list(blank=FALSE, width.cutoff=55))
oldoptions <- options(digits=5)
```

The package `ATEHonest` implements honest confidence intervals and estimators
for estimating average treatment effects under unconfoundedness from @ak17ate.
Here we illustrate the use of the package using NSW data from @DeWa99.

The data is shipped with the package, as two data frames, `NSW` (where the
treated units are from the experimental sample and control units are from PSID),
and `NSWexper`, where both treated and control units are from the experimental
sample. We'll use the experimental sample here.

First we extract the design matrix, and the treatment and outcome vectors:

```{r}
library("ATEHonest")
X <- as.matrix(NSWexper[, 2:10])
d <- NSWexper$treated
y <- NSWexper$re78
```

Next, we compute matrix of distances between treated and control units, using
the same weight matrix to compute distances as in @ak17ate:
```{r}
Ahalf <- diag(c(0.15, 0.6, 2.5, 2.5, 2.5, 0.5, 0.5, 0.1, 0.1))
D0 <- distMat(X, Ahalf, method="manhattan", d)
```

We now compute the first few steps of the solution path. 120 steps will be
sufficient for computing the optimal estimator.

```{r}
op <- ATTOptPath(y, d, D0, maxsteps=120)
```

Next, construct a distance matrix used by the nearest neighbor variance
estimator to estimate the conditional variance of the outcome. We use
Mahalanobis distance:

```{r}
DM <- distMat(X, chol(solve(cov(X))), method="euclidean")
```

Given the solution path, we now compute the root mean squared error optimal
estimator, as well as estimator that's optimal for constructing two-sided CIs:

```{r}
ATTOptEstimate(op, C=1, DM=DM, opt.criterion="RMSE")
ATTOptEstimate(op, C=1, DM=DM, opt.criterion="FLCI")
```

For computing efficiency of one- and two-sided CIs at smooth functions (see
Appendix A in @ak17ate), the solution path is not long enough:

```{r}
ATTEffBounds(op, DM=DM, C=1)
```
We therefore make it longer, by passing the output `op` as an argument to `ATTOptPath`

```{r}
op <- ATTOptPath(path=op, maxsteps=290)
ATTEffBounds(op, DM=DM, C=1)
```

For comparison, we also consider matching estimators. First, a matching
estimator with a single match:
```{r}
ATTMatchEstimate(ATTMatchPath(y, d, D0, M=1, tol=1e-12), C=1, DM=DM)
```

Next, we optimize the number of matches. For that we first compute the matching
estimator for a vector of matches `M`, and then optimize the number of matches
using `ATTMatchEstmate`:
```{r}
mp <- ATTMatchPath(y, d, D0, M=1:10, tol=1e-12)
ATTMatchEstimate(mp, C=1, DM=DM, opt.criterion="FLCI")
ATTMatchEstimate(mp, C=1, DM=DM, opt.criterion="RMSE")
```

We can see that a single match is in fact optimal for both estimation and
construction of two-sided CIs.

```{r cleanup, include=FALSE}
options(oldoptions)
```

# References
