---
title: "Honest CIs: NSW example"
author: "Michal Kolesár"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Inference for Average Treatment Effects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include=FALSE, cache=FALSE}
library("knitr")
knitr::opts_knit$set(self.contained = FALSE)
knitr::opts_chunk$set(tidy = TRUE, collapse=TRUE, comment = "#>",
                      tidy.opts=list(blank=FALSE, width.cutoff=55))
```

The package `ATEHonest` implements honest inference for estimating average
treatment effects under unconfoundedness. Here we illustrate the use of the
package using NSW data.


The data is shipped with the package, as a data frame called `NSW`. First we
extract the design matrix, and the treatment and outcome vectors:

```{r}
library("ATEHonest")
X <- as.matrix(NSW[, 2:10])
## weight matrix
Ahalf <- diag(c(0.15, 0.6, 2.5, 2.5, 2.5, 0.5, 0.5, 0.1, 0.1))
d <- NSW$treated
y <- NSW$re78

## Compute matrix of distances between treated and control units
D0 <- distMat(X, d, Ahalf, method="manhattan", FullMatrix=FALSE)
```

Next, compute distance matrix for variance estimation, and compute NN variance estimator:
```{r}
Avar <- chol(solve(cov(X)))
DMvar <- distMat(X, d, Avar, method="euclidean",
                 FullMatrix=TRUE)
sigma2 <- nnvar(DMvar, d, y, J=30)
```

The first 1,500 steps of the homotopy can be computed by running `nswhomotopy <-
ATTh(D0, maxiter=1500)`. Since  this takes about 10mins on
a desktop computer, the package has a pre-computed solution stored.
```{r}
## throw away the first few steps for which delta is zero
res <- nswhomotopy$res[nswhomotopy$res[, "delta"]>0, ]
## Normalize delta by standard deviation so it's compatible with the paper:
res[, "delta"] <- res[, "delta"]/sqrt(mean(sigma2))

## res contains the optimal weights, use them to compute the estimator and CIs:
rr <- as.data.frame(ATTpath(res, d, y, C=1, mean(sigma2)))
```
At the last step the value of $\delta$ is given by
```{r}
res[nrow(res), "delta"]
```

# Graphs and tables for paper

Now plot like the one in Figure 5:

```{r fig.width=4.5, fig.height=6.5, fig.cap="Reproduction of Figure 5 in the paper"}
## See Figures 1 and 2 below for output
d1 <- reshape2::melt(rr[, c(1, 2, 3, 4, 7, 8)],
                          id.vars="delta")

p <- ggplot2::qplot(x=delta, y=value, data=d1, geom="line") +
     ggplot2::facet_grid( variable ~ ., scales="free_y") +
     ggplot2::theme_bw()
p

## Restrict to delta in [0, 10]
d2 <- d1[d1$delta<=10,]

p <- ggplot2::qplot(x=delta, y=value, data=d2, geom="line") +
     ggplot2::facet_grid( variable ~ ., scales="free_y") +
     ggplot2::theme_bw()
p
```

For now, to find optimal estimator, only look at $\delta$ at knot points (and
don't consider values between knot points). We should approximately match
Table 1. Still need to implement optimal one-sided CI:

```{r}
res.opt <- res[c(which.min(rr$rmse), which.min(rr$hl)), ]
## Homoscedastic errors
as.data.frame(ATTpath(res.opt, d, y, C=1, mean(sigma2)))
## Heteroscedastic errors
as.data.frame(ATTpath(res.opt, d, y, C=1, sigma2))
```
