---
output:
  pdf_document:
    citation_package: natbib
    latex_engine: pdflatex
    keep_tex: true
    includes:
        in_header: vignette_head.tex
title: "ATEHonest: Honest CIs for Average Treatment Effects"
author: "Michal Kolesár"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
bibliography: ate-library.bib
vignette: >
  %\VignetteIndexEntry{ATEHonest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, cache=FALSE}
library("knitr")
knitr::opts_knit$set(self.contained = FALSE)
knitr::opts_chunk$set(tidy = TRUE, collapse=TRUE, comment = "#>",
                      tidy.opts=list(blank=FALSE, width.cutoff=55))
```

The package `ATEHonest` implements honest confidence intervals and estimators
for estimating average treatment effects under unconfoundedness from @ak17ate.
Here we illustrate the use of the package using NSW data from @dw99.

The data is shipped with the package, as two data frames, `NSW` (where the
treated units are from the experimental sample and control units are from PSID),
and `NSWexper`, where both treated and control units are from the experimental
sample. We'll use the experimental sample here.

First we extract the design matrix, and the treatment and outcome vectors, and
we construct a nearest neighbor estimate of the variance of the regression
errors using Mahalanobis distance:

```{r}
library("ATEHonest")
X <- as.matrix(NSWexper[, 2:10])
d <- NSWexper$treated
y <- NSWexper$re78
DMvar <- distMat(X, chol(solve(cov(X))), method="euclidean")
sigma2 <- nnvar(DMvar, d, y, J=3)
```

Next, we compute matrix of distances between treated and control units, using
the same weight matrix to compute distances as in @ak17ate:
```{r}
Ahalf <- diag(c(0.15, 0.6, 2.5, 2.5, 2.5, 0.5, 0.5, 0.1, 0.1))
D0 <- distMat(X, Ahalf, method="manhattan", d)
```

We now compute the first few steps of the solution path. 150 steps will be
sufficient for computing the optimal estimator. Given the solution path, we then
compute the root mean squared error optimal estimator, as well as estimator
that's optimal for constructing two-sided CIs:

```{r}
res <- ATTh(D0, maxiter=150)$res
op <- ATTOptPath(res, y, d)
ATTOptEstimate(op, mean(sigma2), C=1, sigma2final=sigma2, opt.criterion="RMSE")
ATTOptEstimate(op, mean(sigma2), C=1, sigma2final=sigma2, opt.criterion="FLCI")
```

Efficiency of one- and two-sided CIs at smooth functions (see Appendix A in @ak17ate) is:
```{r}
ATTEffBounds(res, d, mean(sigma2), C=1)
```

For comparison, we also consider matching estimators. First, a matching
estimator with a single match:

```{r}
ATTMatchEstimate(ATTMatchPath(y, d, D0, M=1, tol=1e-12), mean(sigma2), C=1, sigma2final=sigma2)
```

Next, we optimize the number of matches. For that we first compute the matching
estimator for a vector of matches `M`, and then optimize the number of matches
using `ATTMatchEstmate`:

```{r}
mp <- ATTMatchPath(y, d, D0, M=1:10, tol=1e-12)
ATTMatchEstimate(mp, mean(sigma2), C=1, sigma2final=sigma2, opt.criterion="FLCI")

ATTMatchEstimate(mp, mean(sigma2), C=1, sigma2final=sigma2, opt.criterion="RMSE")
```
We can see that a single match is in fact optimal for both estimation and construction of two-sided CIs.
